The evolution of the transcriptome of mammalian placentas

### 2016-09-10 manuscript/manuscript.Rnw
update methods

  \textbf{Methods}

  \textbf{Results} We measured the expression profiles of
  \Sexpr{star.logs[,length(unique(file))]} term placentas of
  \Sexpr{star.logs[,length(unique(species))]} species of mammals 
  also identified genes which are expressed in all placentas,
  including genes with immune-modulating properties (\textit{ANXA2},
  \textit{ANXA1}, \textit{S100A11}, and \textit{S100A10}) and
  cell-cell interactions (\textit{LAMC1}, \textit{LUM}, and
  \textit{LGALS1}).

>>>>

  \textbf{Method} Using RNA-seq, we measured the expression profiles
  of \Sexpr{star.logs[,length(unique(file))]} term placentas of
  \Sexpr{star.logs[,length(unique(species))]} species of mammals.

  \textbf{Results} We identified a set of
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  core genes which are expressed (FPKM $\ge 10$) in all placentas.

  including genes with immune-modulating properties (\textit{ANXA2},
  \textit{ANXA1}, \textit{S100A11}, and \textit{S100A10}) and
  cell-cell interactions (\textit{LAMC1}, \textit{LUM}, and
  \textit{LGALS1}).
